Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-10-01 manuscript/manuscript.Rmd
Organizing plots into right folder to add to manuscript.Rmd
Added plots into marginal.Rmd with interpretations.

![Causal diagram showing causes of donor behavior. D = donation to NGO (outcome); G = NGO-government relationship, I = NGO issue area, F = NGO funding source, O = NGO organizational and managerial practices.](output/figures/causal-path-full.pdf){#fig:big-dag}

@@

- First set of questions (hypotheses) can be answered using the results of the intercept-only model.
- Second set of questions (confirmatory) can be answered using the following upper-level models:
  - Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
  - Political ideology: `Donation preferences ~ Political ideology`
  - Social views: `Donation preferences ~ Public affairs trust + Social ideology + Religiosity`
  - Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
  - Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`
  - `Donation preferences ~ (Public affairs) + (Political ideology)`
  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views)`
  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism)`
  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism) + (Demographics)`
- Third set of questions (exploratory) can be answered using a market simulator.

>>>>

![Causal diagram showing causes of donor behavior. D = donation to NGO (outcome); G = NGO-government relationship, I = NGO issue area, F = NGO funding source, O = NGO organizational and managerial practices.](output/figures/causal-path.pdf){#fig:big-dag}

@@

- First set of questions (hypotheses) can be answered using the results of the intercept-only model.

![Combined Results](output/figures/combined-results.png)
We hypothesized that each of these structural and organizational characteristics would have a significant effect on donor behavior, though we were unsure of the direction of that effect.

The following plots zoom in on how strongly each of the attributes serve as heuristics.

![Relationship With Host Government](output/figures/relationship-with-gov.png)
Donors are less likely to donate when government is under crackdown than when it is criticized. In both cases, there is a clear negative effect.

![Organizational Characteristics: Managerial Practices](output/figures/managerial-practices.png)
Donors are more likely to donate when organizations are accountable and financially transparent.

![Organizational Characteristics: Funding Sources](output/figures/funding-sources.png)
Donors are less likely to donate when an NGO is subsidized by government grants, and even less likely when an NGO is funded by a few private donors. (look further into demographic info to see if there is any explanation or insight there)

![Organizational Characteristics: Issue Areas](output/figures/issue-areas.png)
* Emergency response is mentioned in Hypothesis but isn't included in plot?
Issue Areas

![Organization](output/figures/organization.png)
All organizations were percieved positively by respondents. The Red Cross was significantly more favored.

- Second set of questions (confirmatory) can be answered using the following upper-level models:
  - Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
  - Political ideology: `Donation preferences ~ Political ideology`
  - Social views: `Donation preferences ~ Public affairs trust + Social ideology + Religiosity`
  - Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
  - Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`
  - `Donation preferences ~ (Public affairs) + (Political ideology)`
  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views)`
  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism)`
  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism) + (Demographics)`
- Third set of questions (exploratory) can be answered using a market simulator.
